Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-15 cloneoverflow-latex/cloneoverflow.tex
Updated sankey and latex to reflect changes to 2 new projects

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
		\hline 
		\hline 
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 80 & 0 & 336 & 16 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
		\hline
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
		\hline
	\end{tabular} 
	}
\end{table*}

@@

\begin{table}
	\centering
	\caption{Statistics of non-agreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline + reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
		\hline
	\end{tabular} %
	}
\end{table}

@@

%\subsection{Summary of true online clone pairs}
\begin{table}[H]
	\centering
	\caption{Numbers of true positive online clone pairs found by manual investigation}
	\label{tab:classification_true_pairs_summary}
	\small
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Tool & A & A' & B & C & Total \\
		\hline
		good-pairs & 1 & 0 & 4 & 3 & 8 \\
		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
		Simian$_{df}$ pairs & 80 & 0 & 336 & 16 & 432 \\
		NiCad$_{df}$ pairs & 8 & 0 & 27 & 1 & 36 \\
		\hline 
		Total & 97 & 0 & 396 & 30 & 523 \\
		\hline
	\end{tabular} 
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Sankey_proj}
	\caption{Relationships of 53 Stack Overflow clone pairs to their original projects. 49 are outdated and 4 are deleted (shown using (d) suffix).}
	\label{fig:sankey}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Results from a manual investigation of 84 category-A online clone pairs}
	\label{tab:stale_code}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Project & Pairs & Stale & Fresh & Del. & Others \\
		\hline
		ant & 1 & 0 & 1 & 0 & 0 \\
		log4j & 4 & 0 & 4 & 0 & 0 \\
		tomcat & 7 & 7 & 0 & 0 & 0 \\
		aspectj & 2 & 2 & 0 & 0 & 0 \\
		hadoop & 14 & 9 & 5 & 0 & 0 \\
		hibernate & 16 & 4 & 11 & 1 & 0 \\
		jasperreports & 2 & 2 & 0 & 0 & 0 \\
		jfreechart & 4 & 4 & 0 & 0 & 0 \\
		jgraph & 5 & 4 & 0 & 0 & 1 \\
		jgrapht & 1 & 0 & 1 & 0 & 0 \\
		jstock & 2 &  2 & 0 & 0 & 0 \\
		jung & 2 & 2 & 0 & 0 & 0 \\
		junit & 3 & 3 & 0 & 0 & 0 \\
		poi & 3 & 1 & 2 & 0 & 0 \\
		spring & 14 & 9 & 3 & 2 & 0 \\
		struts & 1 & 1 & 0 & 0 & 0 \\
		weka & 3 & 0 & 3 & 0 & 0 \\
		\hline
		Total & 84 & 50 & 30 & 3 & 1 \\
		\hline
	\end{tabular} 
%}
\end{table}

@@

	\caption{53 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}

@@

		3 & hadoop-1.0.0 & DBCountPageView.java & Apache-2 & 21702608 & alteration & 2011-06-12 \\
		4 & hadoop-1.0.0 & DBCountPageView.java & Apache-2 & 21702608 & alteration & 2011-06-12 \\
		5 & hadoop-1.0.0 & JobSubmissionFiles.java & Apache-2 & 14845581 & alteration & 2012-06-25 \\
		6 & hadoop-1.0.0 & LineRecordReader.java & Apache-2 & 16180910 & alteration & 2011-07-25 \\
		7 & hadoop-1.0.0 & LineRecordReader.java & Apache-2 & 16180910 & alteration & 2011-07-25 \\
		8 & hadoop-1.0.0 & StringUtils.java & Apache-2 & 801987 & alteration & 2013-02-04 \\
		9 & hadoop-1.0.0 & TestJobCounters.java & Apache-2 & 18833798 & alteration & 2011-06-12 \\
		10 & hadoop-1.0.0 & TextOutputFormat.java & Apache-2 & 16928749 & alteration & 2011-06-12 \\
		11 & hadoop-1.0.0 & WritableComparator.java & Apache-2 & 22315734 & alteration & 2014-11-20 \\
		12 & hibernate-4.2.2 & ConnectionProviderInitiator.java & -- & 15168494 & alteration & 2012-06-24 \\
		13 & hibernate-4.2.2 & Example.java & -- & 24924255 & alteration & 2013-04-23 \\
		14 & hibernate-4.2.2 & SchemaUpdate.java & -- & 23520731 & alteration & 2016-02-05 \\
		15 & hibernate-4.2.2 & SettingsFactory.java & -- & 8257554 & removal & 2011-03-11 \\
		16 & hibernate-4.2.2 & SQLServer2005LimitHandler.java & -- & 23967852 & alteration & 2015-03-12 \\
		17 & jasperreports-3.7.4 & JRVerifier.java & GLGPLv3+ & 8037824 & alteration & 2008-04-17 \\
		18 & jasperreports-3.7.4 & JRVerifier.java & GLGPLv3+ & 8037824 & alteration & 2011-05-20 \\
		19 & jfreechart-1.0.13 & AbstractXYItemRenderer.java & GLGPLv2.1+ & 12936580 & alteration & 2016-02-19 \\
		20 & jfreechart-1.0.13 & KeyToGroupMap.java & GLGPLv2.1+ & 16058183 & alteration & 2013-07-03 \\
		21 & jfreechart-1.0.13 & SpiderWebPlot.java & GLGPLv2.1+ & 21998949 & alteration & 2008-06-02 \\
		22 & jfreechart-1.0.13 & SpiderWebPlot.java & GLGPLv2.1+ & 21998949 & alteration & 2008-06-02 \\
		23 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
		24 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
		25 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
		26 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
		27 & jstock-1.0.7c & GoogleMail.java & GPLv2+ & 14940863 & alteration & 2015-12-13 \\
		28 & jstock-1.0.7c & GoogleMail.java & GPLv2+ & 24680923 & alteration & 2015-12-13 \\
		29 & jung2-2\_0\_1 & ShortestPathDemo.java & -- & 6025026 & alteration & 2010-04-13 \\
		30 & jung2-2\_0\_1 & ShortestPathDemo.java & -- & 6025026 & alteration & 2010-04-13 \\
		31 & junit-4 & Assert.java & -- & 23586872 & alteration & 2015-05-12 \\
		32 & junit-4 & ExternalResource.java & -- & 7504040 & alteration & 2016-06-25 \\
		33 & junit-4.11 & ExpectException.java & -- & 8802082 & alteration & 2014-05-26 \\
		34 & poi-3.6-20091214 & WorkbookFactory.java & Apache-2 & 12593810 & alteration & 2015-04-29 \\
		35 & spring-framework-3.0.5 & AnnotationMethodHandlerExceptionResolver.java & Apache-2 & 5660519 & removal & 2012-01-20 \\
		36 & spring-framework-3.0.5 & AutowireUtils.java & Apache-2 & 20913543 & alteration & 2014-10-28 \\
		37 & spring-framework-3.0.5 & CustomCollectionEditor.java & Apache-2 & 18623736 & alteration & 2013-11-21 \\
		38 & spring-framework-3.0.5 & DefaultAnnotationHandlerMapping.java & Apache-2 & 3758110 & removal & 2012-01-20 \\
		39 & spring-framework-3.0.5 & DefaultPropertiesPersister.java & Apache-2 & 6149818 & alteration & 2013-03-19 \\
		40 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2016-07-15 \\
		41 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2008-12-18 \\
		42 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2008-12-18 \\
		43 & spring-framework-3.0.5 & DispatcherServlet.java & Apache-2 & 4781746 & alteration & 2011-08-08 \\
		44 & spring-framework-3.0.5 & Jaxb2Marshaller.java & Apache-2 & 10924700 & alteration & 2012-08-28 \\
		45 & spring-framework-3.0.5 & ScheduledTasksBeanDefinitionParser.java & Apache-2 & 3751463 & alteration & 2016-07-05 \\
		46 & struts2-2.2.1 & DefaultActionMapper.java & Apache-2 & 14019840 & alteration & 2013-10-18 \\
		47 & tomcat-7.0.2 & BasicAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
		48 & tomcat-7.0.2 & BasicAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
		49 & tomcat-7.0.2 & CoyoteAdapter.java & Apache-2 & 24404964 & alteration & 2012-11-18 \\
		50 & tomcat-7.0.2 & CoyoteAdapter.java & Apache-2 & 24404964 & alteration & 2012-11-18 \\
		51 & tomcat-7.0.2 & FormAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
		52 & tomcat-7.0.2 & HttpServlet.java & Apache-2 & 5266856 & alteration & 2011-10-22 \\
		53 & tomcat-7.0.2 & JspRuntimeLibrary.java & Apache-2 & 10289462 & alteration & 2012-09-12 \\

@@

%The single missing Stack Overflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian. It is removed from the results of the pretty-printed version because it is an outlier. The rest are missing because of different parameter settings.

>>>>

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
		\hline 
		\hline 
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 19 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
		\hline
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
		\hline
	\end{tabular} 
	}
\end{table*}

@@

\begin{table}
	\centering
	\caption{Statistics of non-agreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
		\hline
	\end{tabular} %
	}
\end{table}

@@

%\subsection{Summary of true online clone pairs}
\begin{table}[H]
	\centering
	\caption{Numbers of true positive online clone pairs found by manual investigation}
	\label{tab:classification_true_pairs_summary}
	\small
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Tool & A & A' & B & C & Total \\
		\hline
		good-pairs & 1 & 0 & 4 & 3 & 8 \\
		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
		Simian$_{df}$ pairs & 79 & 0 & 336 & 17 & 432 \\
		NiCad$_{df}$ pairs & 8 & 0 & 27 & 1 & 36 \\
		\hline 
		Total & 96 & 0 & 396 & 31 & 523 \\
		\hline
	\end{tabular} 
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{Sankey_proj}
	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
	\label{fig:sankey}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Results from a manual investigation of 84 category-A online clone pairs}
	\label{tab:stale_code}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Project & Pairs & Stale & Fresh & Del. & Others \\
		\hline
		ant & 1 & 0 & 1 & 0 & 0 \\
		log4j & 4 & 0 & 4 & 0 & 0 \\
		tomcat & 7 & 7 & 0 & 0 & 0 \\
		aspectj & 2 & 2 & 0 & 0 & 0 \\
		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
		hadoop & 14 & 9 & 5 & 0 & 0 \\
		hibernate & 16 & 4 & 11 & 1 & 0 \\
		jasperreports & 2 & 2 & 0 & 0 & 0 \\
		jfreechart & 4 & 4 & 0 & 0 & 0 \\
		jgraph & 5 & 4 & 0 & 0 & 1 \\
		jgrapht & 1 & 0 & 1 & 0 & 0 \\
		jstock & 2 &  2 & 0 & 0 & 0 \\
		jung & 2 & 2 & 0 & 0 & 0 \\
		junit & 3 & 3 & 0 & 0 & 0 \\
		poi & 3 & 1 & 2 & 0 & 0 \\
		spring & 14 & 9 & 3 & 2 & 0 \\
		struts & 1 & 1 & 0 & 0 & 0 \\
		weka & 3 & 0 & 3 & 0 & 0 \\
		\hline
		Total & 96 & 55 & 37 & 3 & 1 \\
		\hline
	\end{tabular} 
%}
\end{table}

@@

	\caption{58 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}

@@

			3 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1 & 2513183 & alteration  &  2015-03-17 \\
			4 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
			5 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
			6 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  & 2011-03-01 \\
			7 & eclipse-SDK  & WizardDialog.java  & EPLv1  &   11861598	 & alteration  &  2011-02-03 \\
			8 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
			9 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & Apache-2 & 14845581 & alteration  & 2012-06-25 \\
			11 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
			12 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
			13 & hadoop-1.0.0  & StringUtils.java  & Apache-2 & 801987 & alteration  & 2013-02-04 \\
			14 & hadoop-1.0.0  & TestJobCounters.java  & Apache-2 & 18833798 & alteration  & 2011-06-12 \\
			15 & hadoop-1.0.0  & TextOutputFormat.java  & Apache-2 & 16928749 & alteration  & 2011-06-12 \\
			16 & hadoop-1.0.0  & WritableComparator.java  & Apache-2 & 22315734 & alteration  & 2014-11-20 \\
			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & -- & 15168494 & alteration  & 2012-06-24 \\
			18 & hibernate-4.2.2  & Example.java  & -- & 24924255 & alteration  & 2013-04-23 \\
			19 & hibernate-4.2.2  & SchemaUpdate.java  & -- & 23520731 & alteration  & 2016-02-05 \\
			20 & hibernate-4.2.2  & SettingsFactory.java  & -- & 8257554 & removal  & 2011-03-11 \\
			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & -- & 23967852 & alteration  & 2015-03-12 \\
			22 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2008-04-17 \\
			23 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2011-05-20 \\
			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & GLGPLv2.1+ & 12936580 & alteration  & 2016-02-19 \\
			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & GLGPLv2.1+ & 16058183 & alteration  & 2013-07-03 \\
			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
			28 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			29 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			30 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			31 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
			32 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 14940863 & alteration  & 2015-12-13 \\
			33 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 24680923 & alteration  & 2015-12-13 \\
			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
			36 & junit-4  & Assert.java  & -- & 23586872 & alteration  & 2015-05-12 \\
			37 & junit-4  & ExternalResource.java  & -- & 7504040 & alteration  & 2016-06-25 \\
			38 & junit-4.11  & ExpectException.java  & -- & 8802082 & alteration  & 2014-05-26 \\
			39 & poi-3.6-20091214  & WorkbookFactory.java  & Apache-2 & 12593810 & alteration  & 2015-04-29 \\
			40 & spring-framework-3.0.5  & AnnotationMethodHandlerExceptionResolver.java  & Apache-2 & 5660519 & removal  & 2012-01-20 \\
			41 & spring-framework-3.0.5  & AutowireUtils.java  & Apache-2 & 20913543 & alteration  & 2014-10-28 \\
			42 & spring-framework-3.0.5  & CustomCollectionEditor.java  & Apache-2 & 18623736 & alteration  & 2013-11-21 \\
			43 & spring-framework-3.0.5  & DefaultAnnotationHandlerMapping.java  & Apache-2 & 3758110 & removal  & 2012-01-20 \\
			44 & spring-framework-3.0.5  & DefaultPropertiesPersister.java  & Apache-2 & 6149818 & alteration  & 2013-03-19 \\
			45 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2016-07-15 \\
			46 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
			47 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
			48 & spring-framework-3.0.5  & DispatcherServlet.java  & Apache-2 & 4781746 & alteration  & 2011-08-08 \\
			49 & spring-framework-3.0.5  & Jaxb2Marshaller.java  & Apache-2 & 10924700 & alteration  & 2012-08-28 \\
			50 & spring-framework-3.0.5  & ScheduledTasksBeanDefinitionParser.java  & Apache-2 & 3751463 & alteration  & 2016-07-05 \\
			51 & struts2-2.2.1  & DefaultActionMapper.java  & Apache-2 & 14019840 & alteration  & 2013-10-18 \\
			52 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
			53 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
			54 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
			55 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
			56 & tomcat-7.0.2  & FormAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
			57 & tomcat-7.0.2  & HttpServlet.java  & Apache-2 & 5266856 & alteration  & 2011-10-22 \\
			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & Apache-2 & 10289462 & alteration  & 2012-09-12 \\

@@

%The single missing Stack Overflow fragment (19051537\) (denoted by *) is one of the 11 false clones generated by Simian. It is removed from the results of the pretty-printed version because it is an outlier. The rest are missing because of different parameter settings.
